---
title: "Predicting Fatalities from Vehicle Accidents in New Zealand"
author: "Vincent Lee"
date: "August 27, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This application allows us to predict the fatalities that arises from motor accidents in New Zealand based on the number of population at given particular year. 

The data is sourced from the Ministry of Transport, New Zealand. This statistics is compiled up to 2015. 

To know more, please check out their website: 
<http://www.transport.govt.nz/research/roadcrashstatistics/motorvehiclecrashesinnewzealand/>.

## How does the data looks like?

```{r, echo=FALSE}
##the dataset is named as NZCrashes
library(readxl)
NZCrashes <- read_excel("C:/Users/USER/Desktop/NZCrashes.xls")
```



```{r crashes, echo = TRUE}

summary(NZCrashes)
```


## Fitting prediction models

- The model used is the linear regression model between population and fatatilies and we can compare between the predicted and the actual figures.

```{r, echo= TRUE}
model1 <- lm(NumberofFatalities ~ Per100000Population, data = NZCrashes)
plot(model1)
```

```{r, echo = TRUE}
plot(NZCrashes$Per100000Population, NZCrashes$NumberofFatalities,
            xlab ="Population per 100000", ylab= "No of fatalities", xlim = c(249,773), ylim =c(232, 843))
```


## Application to visualise the prediction model

Please check out the application for the results of the prediction model:
<https://ivince20x4.shinyapps.io/predictnzfatalities/>

You can change the population figure to find out the predicted value for the number of fatalities. 

